---
title       : Generalized Linear Models (GLMs)
subtitle    : 
author      : Brandon Hu
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## What are Generalized Linear Models?

Extensions of traditional regression models which:
* Allow the mean to depend on the explanatory variables through a link function 
* Response variable to be any member of a set of distributions

In R we can use:
* The function glm() to work with generalized linear models

---

## Why Linear Regression?

* Easy to use
* Easy to interpret
* Applicable for a huge variety of problems
* Fairly accurate

$\Rightarrow$ Most widely used algorithms by data scientists

```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.align = 'center'}
library(ggplot2)
p <- ggplot(swiss, aes(Fertility, Infant.Mortality))
p <- p + geom_point() + stat_smooth(method = "lm")
p <- p + xlab("") + ylab("")
p
```

---

## Why GLM?

* Response variable has lots of problems with discrete outcomes
* Error models have to stay interpretable even when the outcome has to be positive
* To demonstrate linear gression with multiple predictors - Swiss Data Model (refer to next slide for the application which show case it)

```{r, echo = FALSE}
glm(Infant.Mortality ~ Fertility + Education + Catholic, data = swiss)
```

---

## Developed Application

Developed an application to allow one to learn about GLM:
* Without R knowledge 
* To focus on the algorithm
* Test out with different predictors and compare their effects

<center><img src=./assets/img/main.png height='60%' width='60%' style='margin:0px; border: 2px solid #FF0000'/></center>

<center>https://s-bolz.shinyapps.io/Developing-Data-Products-Assignment/</center>

